\begin{biblio}

\bibitem{Alenmyr}
Alenmyr, S. Model Predictive Control for Stock Postfolio Selection / S.~Alenmyr, A.~Ogren  //MSc Theses. – 2010.

\bibitem{Boyd}
Boyd, S. Vandenberghe L. Convex optimization. -- Cambridge university press, 2004.

\bibitem{ChenAllgower} 
Chen, H. A quasi-infinite horizon nonlinear model predictive control scheme with guaranteed stability / H. Chen, F. Allg\"{o}wer // Automatica -- 1998. -- Vol. 34, no. 10. -- P. 1205–-1217.


\bibitem{Mayne2000}
Constrained model predictive control: Stability and optimality / D.Q. Mayne [et. al]  // Automatica. -- 2000. -- Vol.~36, no.~6. -- P.~{789-814}.

\bibitem{Dombrovskii}
Dombrovskii, V. Dynamic Investment Portfolio Optimization under Constraints in the Financial Market with Regime Switching using Model Predictive Control / V.~Dombrovskii, T.~Obyedko  //arXiv preprint arXiv:1410.1136. -– 2014.

\bibitem{Fitria}
Fitria, I. Investment ManagementUsing Portfolio Optimizationwith Stock Price Forecasting/ I.~Fitria, E.~Apriliani, E.R.M.~Putri  //Applied Mathematical Sciences. – 2016. P.~{2405-2413}.

\bibitem{Grune}
Gr\"{u}ne, L. Analysis and design of unconstrained nonlinear MPC schemes for finite and infinite dimensional systems / L.Grune // SIAM Journal on Control and Optimization. -- 2009. -- Vol. 48, no. 2. -- P. 1206–-1228.

\bibitem{GrunePannek}
Gr\"{u}ne, L. Nonlinear model predictive control / L. Gr\"{u}ne, J. Pannek  -- Springer London, 2011.

\bibitem{Fontes}
Fontes, F.A.C.C. A general framework to design stabilizing nonlinear model predictive controllers / F.A.C.C. Fontes // Systems \& Control Letters. -- 2001. -- Vol.~42. -- No.~2. -- P. 127--143.

\bibitem{Herzog}
Herzog, F. Model predictive control for portfolio selection /  F.~Herzog [et. al] //American Control Conference, 2006. – IEEE, -- 2006. -- P. 8.

\bibitem{Hewing}
Hewing, L. Cautious model predictive control using Gaussian process regression / L.~Hewing , M. N.~Zeilinger  //arXiv preprint arXiv:1705.10702. -– 2017.

\bibitem{Keerthi88}
Keerthi, S.S.  Optimal, infinite horizon feedback laws for a general class of constrained discrete
time systems: Stability and moving-horizon approximations / S.S.~Keerthi,   E.G.~Gilbert  //
Journal of Optimization Theory and Application. -- 1988. -- Vol.~{57}, no.~{2}. -- P.~{265-293}.

\bibitem{Khalil}
Khalil, H.K. Nonlinear systems / H.K. Khalil -- New Jersey: Prentice-Hall, 1996.

\bibitem{Marigo}
Marigo, A. Model predictive control for portfolio optimization / A.~Marigo, B.~Piccoli  //Proc. of 2nd IFAC Symposium on System, Structure and Control. -– 2004.

\bibitem{NocedalWright}
Nocedal, J. Numerical Optimization / J.~Nocedal,  S.J.~Wright. -- Springer Series in Operations
Research, Springer Verlag, 2006.

\bibitem{Nystrup}
Nystrup, P. Multi-period portfolio selection with drawdown control / P.~Nystrup  [et al.] //Annals of Operations Research. – 2017. -- P.~{1--27}.

\bibitem{MayneRawlings}
Rawlings, J.B. Model Predictive Control: Theory and Design / J.B. Rawlings, D.Q.~Mayne. -- Madison:
Nob Hill Publishing, 2009. -- 576 p.

\bibitem{Yamada}
Yamada, Y. Model Predictive Control for Optimal Pairs Trading Portfolio with Gross Exposure and Transaction Cost Constraints / Y.~Yamada, J.A.~Primbs  //Asia-Pacific Financial Markets. – 2018. P.~{1-21}.


\bibitem{AfanasievKolmanovskiNosov}
Афанасьев, В.Н. Математическая теория конструирования систем управления / В.Н. Афанасьев, В.Б. Колмановский, В.Р. Носов -- М.: Высш. шк., 2003.



\bibitem{Bellman}	
Беллман, Р. Динамическое программирование / Р. Беллман. -- М.:Инностранная литература, 1960. -- 400 с.

\bibitem{Borovkov}
Боровков, А.А.  Числовые характеристики случайных величин. 5-е изд. / А.А.~Боровков // М.: Либроком. -- 2009. -- Глава 4.

\bibitem{Vasiliev}
Васильев, Ф.П.	Методы оптимизации


\bibitem{GabasovKirillovaPU}
Габасов, Р. Принципы оптимального управления / Р. Габасов,  Ф.М. Кириллова  // Докл. НАН Беларуси.
-- 2004. -- Т.~48, №~1. -- С.~15-18.


\bibitem{Dantzig}
Данциг, Д. Линейное программирование, его применения и обобщения / Д.~Данциг. -- М.: Прогресс,
1966. -- 600~с.

\bibitem{LeeMarcus} Ли, Э.Б. Основы теории оптимального управления / Э.Б. Ли, Л. Маркус  -- М.: Наука, 1972.

\bibitem{Malkin}
Малкин, И.Г. Теория устойчивости движения. 2-е изд., стереотип / И.Г.~Малкин //М.: Эдиториал УРСС. -– 2004.

\bibitem{Pontryagin}
Математическая теория оптимальных процессов/ Л.С.~Понтрягин [и др.] --  М.: Физматгиз, 1961. 392~с.

\bibitem{Strizhov}
Стрижов, В.В. Методы индуктивного порождения регрессионных моделей / В.В. Стрижов -- М.: Вычислительный центр им. А.А. Дородницына РАН, 2008.


\end{biblio} 